Overlapping Batches for the Assessment of Solution Quality in Stochastic Programs

### 2014-06-22 omrp_lb_rev.tex
Update computational efficiency section

We tested this theoretical relationship using the Newsvendor problem solved with insertion sort.
Insertion sort is an efficient sorting algorithm when the values are already largely sorted. 
Therefore, as overlapping increases, insertion sort results in a decreased solution time per batch for the NVD problem. 
The average computation time per batch was found empirically to be well approximated by power law with $p = 0.71$.
The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency_nv}, where the theoretical computational efficiency, shown in solid line, is repeated from Figure \ref{fig:efficiency_theory}.
It appears that empirical observations match with the theoretical efficiency calculations well.

@@

\begin{figure}[htb!]
	\centering
	\includegraphics[width=.5\textwidth]{images/work_comparison}
	\caption{
		A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
		}
\label{fig:comp_work_comparison}
\end{figure}

@@

>>>>

All theoretical curves in this section were computed using $m = 1000$, but the results do not change substantially with increasing batch size.
Newsvendor computations used $m = 1000$ with $10,000$ replications.

We tested this theoretical relationship using the Newsvendor problem solved with insertion sort.
Insertion sort is an efficient sorting algorithm when the values are already largely sorted. 
Therefore, as overlapping increases, insertion sort results in a decreased solution time per batch for the NVD problem. 
The average computation time per batch was found empirically to be well approximated ($R^2 = 0.994$) by power law with $p = 0.71$.
The empirically measured computational efficiency is compared to the theoretical result in Figure \ref{fig:efficiency_nv}, where the theoretical computational efficiency, shown in solid line, is repeated from Figure \ref{fig:efficiency_theory}.
It appears that empirical observations match with the theoretical efficiency calculations well.

@@

\begin{figure}[htb!]
	\centering
	\subfloat[][]{
	   \label{fig:comp_work_comparison_theory}
	   \includegraphics[width=.5\textwidth]{images/work_comparison}}
	\subfloat[][]{
	   \label{fig:comp_work_comparison_nv}
	   \includegraphics[width=.5\textwidth]{images/nv_work_comparison}}
		\caption{
		(Left) A theoretical comparison of the computational work required to get equivalent variance reduction between OMRP and MRP when the number of batches are increased.
		(Right) Measured computational work for NVD compared with the theoretical results.
		}
\label{fig:comp_work_comparison}
\end{figure}

@@

With these considerations, for situations where $p > 0$ but its size cannot be readily measured or estimated, we recommend selecting a large value of $\gammab$ such as $0.9$.
This allows for some increase in efficiency while remaining robust in the event that $p$ is smaller than expected.
